Proposed Solution

### 2016-11-14 Ennan-Proposal/impact.tex
stuff

Since her beginning of teaching at Yale, the PI is actively including topics from her 
research into her courses (such as ``Software Analysis and Verification''). This way
she motivates undergraduate students to get involved in the research. Until now 
she supervised more than 20 undergraduate student projects. Two students (Reinking, Cai) 
who did an undergraduate research projects with her, are now PhD students at 
UC Berkeley, and two more students are applying (Anklessaria, La) to graduate schools 
this year. Additionally, there are two student startups, which are now supported
by YCombinator, that started under her supervision. Those startup are PatientBank
and Py, an app for learning Python. Some

@@

If successful, \app could have the following broader impacts:

@@

\item {\bf Opening the door of language-based configuration verification.}
  Today's misconfiguration checking approaches are still using {\em ad hoc}
  algorithms to detect potential misconfiguration root causes. On the
  contrary, \app could open the door of configuration verification,
  which rigorously verifies whether the target configuration files meet
  specifications. In other words, \app enables users 
  to verify configuration files like verifying programs. Such a capability
  cannot be offered by any of existing efforts.

\item {\bf Preventing configuration errors without adding any additional
  burden to users.} Because \app employs automatic machine learning 
  algorithms to extract rules, users or system administrators do not need
  to manually write their specifications, which significantly reduce the
  burden of users and system administrators. Such a way not only
  makes the configuration verification process become much easier and more 
  usable, but also decreases the potential issues of writing 
  specifications.

\item {\bf Complementing post-failure error diagnosis efforts.}
  There have been many diagnosis and troubleshooting efforts to localizing
  the root causes of configuration errors after system failures occur.
  We call these approaches as post-failure error diagnosis efforts.
  On the contrary, \app offers a pre-failure error checking effort,
  which could be looked as a preliminary checking before installing
  systems. Because \app is able to find out many sophisticated 
  configuration errors, it removes many labors of 
  the post-failure error diagnosis tools. In addition, the results
  output by \app could be used as a guidance for all the post-failure
  error diagnosis approaches, making these approaches more efficient.

>>>>

Since her beginning of teaching at Yale, the PI is actively including topics from her 
research into her courses (such as ``Software Analysis and Verification''). This way
she motivates undergraduate students to get involved in the research. Until now 
she supervised more than 20 undergraduate student projects. Two students (Reinking, Cai) 
who did an undergraduate research projects with her, are now PhD students at 
UC Berkeley, and two more students are applying (Anklessaria, La) to graduate schools 
this year. Additionally, there are two student startups, which are now supported
by YCombinator, that started under her supervision. Those startup are PatientBank
and Py, an app for learning Python.

@@

We believe that \app could have the following broader impacts:

@@

\item {\bf Enabling language-based configuration verification.}
  Today's misconfiguration checking approaches are still using {\em ad hoc}
  algorithms to detect potential misconfiguration root causes. \app 
  should enable more rigorous verification of configuration files. By verification we
  mean checking that the given configuration file adheres to a
  specification.
%\item {\bf Preventing configuration errors without adding any additional
%  burden to users.} Because \app employs automatic machine learning 
%  algorithms to extract rules, users or system administrators do not need
%  to manually write their specifications, which significantly reduce the
%  burden of users and system administrators. Such a way not only
%  makes the configuration verification process become much easier and more 
%  usable, but also decreases the potential issues of writing 
%  specifications.

\item {\bf Complementing post-failure error diagnosis efforts.}
  There have been many diagnosis and troubleshooting efforts to localizing
  the root causes of configuration errors after system failures occur.
  We call these approaches as post-failure error diagnosis efforts.
  \app will offer a pre-failure error checking
  which could be looked as a preliminary checking before installing
  systems. Because \app is able to find out many sophisticated 
  configuration errors, it removes many labors of 
  the post-failure error diagnosis tools. In addition, the results
  output by \app could be used as a guidance for all the post-failure
  error diagnosis approaches, making these approaches more efficient.

### 2016-11-14 Ennan-Proposal/travis.tex
stuff

Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
to hold for correct TravisCI configuration files. Traditionally, 
version space learning builds a model that defines membership using a series of 
disjunctions from a set of predefined hypotheses.  However, we need  to 
use conjunctions to convey that a configuration file is only correct if 
it satisfies all the learned relations. Those rules can be seen as
positive examples in classifying correct files. In addition, we will have
so-called {\emph {breaking rules}} which are derived from the files 
that do not compile, \ie~negative examples. Breaking rules are specified 
using disjunctions.

Figure~\ref{fig:versionSL} shows an example set of necessary and breaking rules that would be learn if the training set contains a failing file with {\small node\_js: 0}, and a passing file with {\small node\_js: 0.4.}
The breaking rules will describe the conditions for an incorrect file based on examples we have seen of incorrect files (red circles).
Likewise, the necessary rules will describe the conditions for a correct file based on examples we have seen of correct files (green pluses).
This results in a space (green stripes) where a file may contain relations that cannot be classified as either breaking or necessary.
Part of the research task will be to find an optimal treatment for such cases.

 Adding this temporal component, 
This extension will build a logical formula representing the entire 
history of examples, and use an SMT solver to find a classification model.

Since a TravisCI configuration file is dependent
on the code and system it is trying to build, 
we must consider a more general sense of configuration file.
We will call this a program summary $P_t$, which is a representation 
of the repository which contains the information 
relevant to the learning process.
The subscript on $P_t$ is a timestamp tag based on 
the ordered git commit history.
%In the case of TravisCI, this include the \verb|.travis.yml| file, 
%as well as code features that may effect build status, 
%such as programming language and a list of imported libraries.
%The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.

>>>>

Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard ConfigC approach to learn the rules that have 
to hold for correct TravisCI configuration files. Traditionally, 
version space learning builds a model that defines membership using a series of 
disjunctions from a set of predefined hypotheses.  However, we need  to 
use conjunctions to convey that a configuration file is only correct if 
it satisfies all the learned relations. Those rules can be seen as
positive examples in classifying correct files. In addition, we will have
so-called {\emph {breaking rules}} which are derived from the files 
that do not compile, \ie~negative examples. Breaking rules are specified 
using disjunctions.

Figure~\ref{fig:versionSL} shows an example set of necessary and breaking rules that would be learned if the training set contains a failing file indicating that 
{\small node\_js} version is 0.2, and a passing file has its version set to 0.4.
With red dots we depict incorrect files that do not compile, and the green crosses show correct files.
From both types of files, we extract breaking and necessary rules, which define borders between those two sets of files.
This results in a space (green stripes) where a file may contain relations that cannot be classified as either breaking or necessary.
For example, if a user provides a file which specifies version 0.3 of {\small node\_js}, this file will fall in the green striped space.
Part of the research task will be to find an optimal classification for such cases.

The success or failure of a TravisCI configuration file is dependent
not only on the configuration file itself (namely, a .travis.yml file) but it also depends on system information such as programming languages and a list of imported libraries.
For this reason, we call this extended configuration files a program summary, denoted with $P_t$. This is a representation 
of the repository which contains any information 
relevant to the learning process.
The subscript on $P_t$ is a timestamp tag based on 
the ordered git commit history.
%In the case of TravisCI, this include the \verb|.travis.yml| file, 
%as well as code features that may effect build status, 
%such as programming language and a list of imported libraries.
%The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.
